### 2020-08-05 data/draft-sections.tex
added \item to activities

\subsection{Other Activities: 2019-20}
\begin{enumerate}
A. K. Nandakumaran was Convener, KVPY
A. K. Nandakumaran was Member, Library Committee
Apoorva Khare was Member of two UG Project Presentation Evaluation Committees
Apoorva Khare was Pre-RMO (Regional Mathematics Olympiad) - helped in setting the question paper
Apoorva Khare was Senate nominee for Comprehensive Exam of Vinayak Ramkumar (student of P. Vijay Kumar, ECE)
Apoorva Khare was Advising: (1) Prateek Kumar Vishwakarma, Int-PhD (passed his Comprehensive Exam) (2) Babhrubahan Bose, Int-PhD (passed his Comprehensive Exam) (3) G.V.K. Teja, PhD (passed his Comprehensive Exam) (4) Swarnalipa Datta, Int-PhD (downgraded to MS) Mentoring: (5) Dr. Projesh Nath Choudhury, NBHM postdoc
Arvind Ayyer was Referee for the thesis of Majil Pratim Saikia at University of Vienna.
Arvind Ayyer was Referee for the thesis of Mr. Jyotirmoy Ganguly at IISER Pune.
Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)
Gautam Bharali was Served as an independent expert for the Swiss National Science Foundation for the review of project proposals in pure mathematics in 2019.
R VENKATESH was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
R VENKATESH was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019). Partially funded by the UGC-CAS grant.  Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting. 
R VENKATESH was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
Siddhartha Gadgil was thesis examiner for a thesis at IIT, Kanpur
Siddhartha Gadgil was thesis examiner for a thesis at Delhi University
Siddhartha Gadgil was thesis examiner for a thesis for TIFR, Mumbai
Siddhartha Gadgil was member of selection committee at BHU
Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
Subhojoy Gupta was Co-organizer of an Advanced Instructional School on Riemannian Geometry, sponsored by the National Centre for Mathematics, held in July 2019.
Subhojoy Gupta was Referee for "Proceedings of the London Mathematical Society", "Journal of Topology", "Manuscripta Mathematica" and reviewer for AMS and Zentralblatt Math Reviews
Subhojoy Gupta was Supervised UG final year project of Shabarish Chenakkod
\end{enumerate}

>>>>

\subsection{Other Activities: 2019-20}
\begin{enumerate}
\item A. K. Nandakumaran was Convener, KVPY
\item A. K. Nandakumaran was Member, Library Committee
\item Apoorva Khare was Member of two UG Project Presentation Evaluation Committees
\item Apoorva Khare was Pre-RMO (Regional Mathematics Olympiad) - helped in setting the question paper
\item Apoorva Khare was Senate nominee for Comprehensive Exam of Vinayak Ramkumar (student of P. Vijay Kumar, ECE)
\item Apoorva Khare was Advising: (1) Prateek Kumar Vishwakarma, Int-PhD (passed his Comprehensive Exam) (2) Babhrubahan Bose, Int-PhD (passed his Comprehensive Exam) (3) G.V.K. Teja, PhD (passed his Comprehensive Exam) (4) Swarnalipa Datta, Int-PhD (downgraded to MS) Mentoring: (5) Dr. Projesh Nath Choudhury, NBHM postdoc
\item Arvind Ayyer was Referee for the thesis of Majil Pratim Saikia at University of Vienna.
\item Arvind Ayyer was Referee for the thesis of Mr. Jyotirmoy Ganguly at IISER Pune.
\item Arvind Ayyer was Thesis examiner for Mr. Sudip Bera, Visva-Bharati University.
\item Gautam Bharali was Member of the executive committee of IWM (Indian Women and Mathematics)
\item Gautam Bharali was Served as an independent expert for the Swiss National Science Foundation for the review of project proposals in pure mathematics in 2019.
\item R VENKATESH was Algebra Symposium, Department of Mathematics, IISc, Bangalore, India (February 12, 2020).
\item R VENKATESH was Discussion Meeting on Representation Theory 2019, Department of Mathematics, IISc, Bangalore (December 14 - 16, 2019). Partially funded by the UGC-CAS grant.  Two lecture series was delivered by Professor Vyjayanthi Chari (UC Riverside, USA) and Professor Anne Schilling (UC Davis, USA) as part of this discussion meeting. 
\item R VENKATESH was NCM - Instructional School for Teachers on Analysis and PDE, Department of Mathematics, IISc, Bangalore (May 6 - 18, 2019). 
\item Siddhartha Gadgil was thesis examiner for a thesis at IIT, Kanpur
\item Siddhartha Gadgil was thesis examiner for a thesis at Delhi University
\item Siddhartha Gadgil was thesis examiner for a thesis for TIFR, Mumbai
\item Siddhartha Gadgil was member of selection committee at BHU
\item Subhojoy Gupta was Member of Research Advisory Committee for Ramya Nair, a PhD student at IISER Pune. 
\item Subhojoy Gupta was Co-organizer of an Advanced Instructional School on Riemannian Geometry, sponsored by the National Centre for Mathematics, held in July 2019.
\item Subhojoy Gupta was Referee for "Proceedings of the London Mathematical Society", "Journal of Topology", "Manuscripta Mathematica" and reviewer for AMS and Zentralblatt Math Reviews
\item Subhojoy Gupta was Supervised UG final year project of Shabarish Chenakkod
\end{enumerate}
